---
title: "Kaggle Survey Overview"
author: "Kumar Suresh Halake"
output: html_notebook
---

```{r,include=FALSE,echo=FALSE,warning=FALSE,error=FALSE}
library(ggplot2)
library(tm)
library(wordcloud)
library(gridExtra)
library(plyr)
library(dplyr)
library(reader)
library(xlsx)
library(reshape2)
```


### Loading datasets
```{r,error=FALSE,eval=TRUE,echo=TRUE,include=TRUE}
fr<-read.csv("./freeformResponses.csv",na.strings =c(NA,""),stringsAsFactors = FALSE)
mcq <- read.csv("./multipleChoiceResponses.csv",na.strings =c(NA,""),stringsAsFactors = FALSE)
schema<-read.csv("./schema.csv",na.strings =c(NA,""),stringsAsFactors = FALSE)
```

### Participation in Survey - Countrywise 

* [Displayed countries having at least 100 respondents]

```{r}
mcq%>%group_by(Country,GenderSelect)%>%tally()%>%filter(n>=100 & !is.na(n))%>%ggplot(aes(reorder(Country,n),n))+
  geom_bar(stat="identity",aes(fill=GenderSelect))+
  theme(legend.position = "bottom")+labs(x="Country",y="Number of Respondents",face="itALICS")+
  scale_y_discrete(expand=c(0,0)) +
  coord_flip()
```

------

### Age distribution of Participants
```{r}
mcq%>%select(Age,GenderSelect)%>%
  mutate(age_group=cut(Age,breaks=c(0,5,10,20,30,40,50,60,70,80,90,100),closed = "right"))%>%
  group_by(age_group,GenderSelect)%>%tally()%>%
  ggplot(aes(age_group,n,fill=GenderSelect))+
  geom_bar(stat="identity")+
  scale_fill_discrete(labels=c("Different identity","Female","Male","Non-binary\ngenderqueer\ngender non conforming","Not specified"))+
  theme(legend.key.height = unit(0.8,"cm"),axis.text.x = element_text(angle=45,hjust=1))+labs(x="Age Group",y="Frequency")
```

------

### Employment Status and Choice of ML tool next year

* [a group having at least 100 respondents are only included]

```{r}
mcq%>%group_by(MLToolNextYearSelect,EmploymentStatus)%>%
  tally()%>%filter(n>=100,!is.na(MLToolNextYearSelect))%>%
  ggplot(aes(reorder(MLToolNextYearSelect,n),n,fill=EmploymentStatus))+
  geom_bar(stat="identity",width=0.9)+
  coord_flip()+
  scale_fill_brewer(labels=c("full tme","part time","prefer not to say","independent contractor/\nfreelancer/\nself employed","not employed/\nnot looking job","not employed/\nlooking job"),palette="Set1")+
  theme(legend.key.height = unit(1,"cm"))+
  scale_y_discrete(expand=c(0,0)) +
  labs(x="Next year choice for ML Tool",y="Frequency")
```

------

```{r}
wordcloud(mcq$MLToolNextYearSelect,colors = rainbow(20))
```



### Employment Status and Choice of ML method next year
* [Each group should have at least 100 respondents]
```{r}
mcq%>%group_by(MLMethodNextYearSelect,EmploymentStatus)%>%tally()%>%
  filter(n>=100,!is.na(MLMethodNextYearSelect))%>%
  ggplot(aes(reorder(MLMethodNextYearSelect,n),n,fill=EmploymentStatus))+geom_bar(stat="identity")+
  coord_flip()+
  scale_fill_brewer(labels=c("full tme","part time","prefer not to say","independent contractor/\nfreelancer/\nself employed","not employed &\nnot looking job","not employed\nlbut ooking job"),palette="Set1")+
  scale_y_discrete(expand=c(0,0)) +
  theme(legend.key.height = unit(1,"cm"))+labs(x="Next year choice for ML method ",y="Frequency")
```

------

```{r}
library(wordcloud)
wordcloud(mcq$MLMethodNextYearSelect,colors = rainbow(10))
```


------


### How many respondents are *Data Scientists* ?
```{r}
mcq%>%group_by(DataScienceIdentitySelect)%>%tally()%>%
  ggplot(aes(reorder(DataScienceIdentitySelect,n),n,color=DataScienceIdentitySelect))+
  geom_segment(aes(xend=DataScienceIdentitySelect,y=0,yend=n),size=3)+
  geom_point(size=6,pch=19)+labs(title="Do you consider\nyourself a data scientist?",x="")+
  theme(legend.position = "none")
```

------

### Association between Undergrad Major subject and self confidence as a *Data Scientist*
```{r}
mcq%>%group_by(MajorSelect,DataScienceIdentitySelect)%>%tally%>%
  filter(!is.na(MajorSelect),!is.na(DataScienceIdentitySelect))%>%
  ggplot(aes(y=MajorSelect,x=DataScienceIdentitySelect,fill=n))+geom_tile()+
  geom_text(aes(label=n),size=2)+
  scale_fill_gradientn(colors=c(low = "white",mid="green",high = "red"))+
  theme(axis.text.x = element_text(angle=90,hjust=1))+
  scale_y_discrete(expand=c(0,0)) +
  labs(x="Do you consider yourself a data scientist?",y="Undergraduate Major")
```


------

### How Partcipants are Learning by various sources

```{r}
p1<-ggplot(mcq,aes(x=LearningCategoryKaggle))+geom_density()+ylim(0,0.06)+labs(x="Kaggle Learning")
p2<-ggplot(mcq,aes(x=LearningCategoryOnlineCourses))+geom_density()+ylim(0,0.06)+labs(x="Online Course learning",y="")
p3<-ggplot(mcq,aes(x=LearningCategoryWork))+geom_density()+ylim(0,0.06)+labs(x="Larning at work",y="")
p4<-ggplot(mcq,aes(x=LearningCategoryUniversity))+geom_density()+ylim(0,0.06)+labs(x="University Learning")
p5<-ggplot(mcq,aes(x=LearningCategorySelftTaught))+geom_density()+ylim(0,0.06)+labs(x="self Learning",y="")
p6<-ggplot(mcq,aes(x=LearningCategoryOther))+geom_density()+ylim(0,0.06)+labs(x="Learning in other ways",y="")

gridExtra::grid.arrange(p1,p2,p3,p4,p5,p6,ncol=3)
```


------

### Current job title of Respondents
```{r}
wordcloud(mcq$CurrentJobTitleSelect,colors = rainbow(15))
```

------

### Percentage Time spent for Data Gathering by a code writer

```{r}
mcq%>%filter(!is.na(TimeGatheringData))%>%
  mutate(gather=cut(TimeGatheringData,breaks = c(-0.05,10,20,30,40,50,60,70,80,90,100),closed="right"))%>%
  group_by(gather)%>%tally()%>%
  ggplot(aes(x=gather,y=n))+
  geom_bar(stat="identity",fill=rainbow(10))+labs(x="% Time",title="Percentage time spent on data gathering")+
  scale_x_discrete(labels=paste0(c("0-10","10-20","20-30","30-40","40-50","50-60","60-70","70-80","80-00","90-100"),"%"))
```

------

### Percentage Time spent for Data visualization by a code writer

```{r}
mcq%>%filter(!is.na(TimeVisualizing))%>%mutate(vizual=cut(TimeVisualizing,breaks = c(-0.05,10,20,30,40,50,60,70,80,90,100),closed="right"))%>%group_by(vizual)%>%tally()%>%
  ggplot(aes(x=vizual,y=n))+geom_bar(stat="identity",fill=rainbow(10))+
  labs(x="% Time",title="Percentage time spent on Vizualisation")+
  scale_x_discrete(labels=paste0(c("0-10","10-20","20-30","30-40","40-50","50-60","60-70","70-80","80-00","90-100"),"%"))
```

------

### Time spent for Model Building by a code writer

```{r}
library(RColorBrewer)
mcq%>%filter(!is.na(TimeModelBuilding))%>%mutate(model=cut(TimeModelBuilding,breaks = c(-0.05,10,20,30,40,50,60,70,80,90,100),closed="right"))%>%group_by(model)%>%tally()%>%
  ggplot(aes(x=model,y=n))+
  geom_bar(stat="identity",fill=brewer.pal(name="Spectral",n=10))+
  labs(x="% Time",title="Percentage time spent on Model Building")+
  scale_x_discrete(labels=paste0(c("0-10","10-20","20-30","30-40","40-50","50-60","60-70","70-80","80-00","90-100"),"%"))
```


------

### Time spent forgetting Insights from data by a code writer

```{r}
mcq%>%filter(!is.na(TimeFindingInsights))%>%mutate(insight=cut(TimeFindingInsights,breaks = c(-0.05,10,20,30,40,50,60,70,80,90,100),closed="right"))%>%group_by(insight)%>%tally()%>%
  ggplot(aes(x=insight,y=n))+
geom_bar(stat="identity",fill=brewer.pal(name="Paired",n=11))+
  labs(x="% Time",title="Percentage time spent for getting Insight from data")+
  scale_x_discrete(labels=paste0(c("0-10","10-20","20-30","30-40","40-50","50-60","60-70","70-80","80-00","90-100"),"%"))
```

------


### The Change in Salary for different empoyements 

```{r}
mcq%>%filter(!is.na(SalaryChange))%>%group_by(SalaryChange)%>%tally()%>%
  ggplot(aes(reorder(SalaryChange,n),n))+geom_bar(stat="identity",fill=rainbow(9),color="black")+
  geom_text(aes(label=paste0(round(n*100/sum(n),2)," %")),size=3,hjust=0)+
  labs(x="Increase / Decrease in Salary",title="Slary Change in Past 3 Years")+
  scale_y_discrete(expand=c(0,0,0.15,0)) +
  scale_x_discrete(expand=c(0,0)) +
  coord_flip()
```

------

### Job Satisfaction level of Employees

```{r}
mcq%>%filter(!is.na(JobSatisfaction))%>%
  group_by(EmploymentStatus,JobSatisfaction)%>%tally()%>%
  ggplot(aes(reorder(JobSatisfaction,n),n,fill=EmploymentStatus))+
  geom_bar(stat="identity",position = "dodge")+
  scale_fill_brewer(labels=c("full tme","part time","prefer not to say","independent contractor/\nfreelancer/\nself employed","not employed &\nnot looking job","not employed\nlbut ooking job"),palette="Dark2")+
  theme(legend.key.height = unit(1,"cm"))+labs(x="Job Satisfaction Level",y="Frequency")+
  scale_y_discrete(expand=c(0,0,0.1,0)) +
  scale_x_discrete(expand=c(0,0)) +
  coord_flip()
```

------

### Most important way to prove the knowledge by learners

```{r}
mcq%>%filter(!is.na(ProveKnowledgeSelect))%>%
  group_by(ProveKnowledgeSelect)%>%tally()%>%
  ggplot(aes(reorder(ProveKnowledgeSelect,n),y=n))+geom_bar(stat="identity",fill=rainbow(7))+
  geom_text(aes(label=paste0(round(n*100/sum(n),2)," %")),hjust=0,size=3)+
  scale_y_discrete(expand=c(0,0,0.1,0)) +
  scale_x_discrete(expand=c(0,0)) +
  labs(x="Way to prove the knowledge by learner")+
  coord_flip()
```


### Influence of learning platform
```{r}
m<-mcq%>%select(starts_with("LearningPlatformUsefulness"))%>%melt(id=0)%>%filter(!is.na(value))

m1<-m
v<-c()
for(i in 1: nrow(m)){
  v[i]<-gsub(x=m$variable[i],pattern = "LearningPlatformUsefulness",replacement = "")
}

m1<-cbind(m1,v)

m1%>%group_by(v,value)%>%tally()%>%ggplot(aes(reorder(v,n),value))+
  geom_tile(aes(fill=n))+
  geom_text(aes(label=n),size=2.5)+
  scale_fill_gradient2(low="white",mid="cyan",high="purple")+
  labs(x="Learning Platform",y="Usefullness",face="italics")+theme(panel.grid = element_blank())+
  scale_y_discrete(expand=c(0,0,0.0,0)) +
  # scale_x_discrete(expand=c(0,0,0)) +
  coord_flip()

```


### Job skill Importance

```{r}
j<-mcq%>%select(starts_with("JobSkillImportance"))%>%melt(id=0)%>%filter(!is.na(value))

j1<-j
u<-c()
for(i in 1: nrow(j)){
  u[i]<-gsub(x=j1$variable[i],pattern = "JobSkillImportance",replacement = "")
}

j1<-cbind(j1,u)

j1%>%group_by(u,value)%>%tally()%>%ggplot(aes(reorder(u,n),value))+
  geom_tile(aes(fill=n))+
  geom_text(aes(label=n),size=2.5)+
  scale_fill_gradient2(low="white",mid="cyan",high="purple")+
  labs(x="Job Skills Importance",y="Usefullness",face="italics",hjust=1)+theme(panel.grid = element_blank())+
  scale_y_discrete(expand=c(0,0,0.1,0)) +
  # scale_x_discrete(expand=c(0,0)) +
  coord_flip()

```

